\textbf{Dynamic Hover Detection:\\Creating GUIs in Elm}

### 2014-01-01 paper/paper.tex
more revisions

The first parameter to \texttt{hoverables} denotes the initial value of the
\texttt{events} signal (signals in Elm must always be defined). The record's
\texttt{hoverable} function is applied to an element and attaches hover
detection to it. Whenever the mouse hovers (or stops hovering) over the element,
an event is fired on the \texttt{events} signal. The value of that event is
determined by the \texttt{(Bool -> a)} parameter of the \texttt{hoverable}
function. In many cases, \texttt{a} will be \texttt{Bool} and the function will
be \texttt{id}. In general, the record's \texttt{hoverable} may be applied
multiple times with all elements it produces reporting their hover information
on \texttt{events}. In this case, \texttt{a} can serve as an identifier, and is
provided by the function argument.

@@

Using only \texttt{hoverable}, we are restricted to one element per signal. With
\texttt{hoverables}, the hover information of an element can be added to an
existing signal, and can even be added during program execution, that is, when
the element is a signal. As the value of a signal of elements changes, we attach
the hover information to the each new element without having to create a new
output signal. We do this by partially applying \texttt{pool.hoverable} to
\texttt{id} purely, and then lifting it on to the argument.

>>>>

The first parameter to \texttt{hoverables} denotes the initial value of the
\texttt{events} signal (signals in Elm must always be defined). The record's
\texttt{hoverable} function is applied to an element and attaches hover
detection to it. Whenever the mouse hovers (or stops hovering) over the element,
an event is fired on the \texttt{events} signal. The value of that event is
determined by the \texttt{(Bool -> a)} parameter of the \texttt{hoverable}
function. In many cases, \texttt{a} will be \texttt{Bool} and the function will
be \texttt{id}. In general, the record's \texttt{hoverable} may be applied
multiple times, with all elements it produces reporting their hover information
on \texttt{events}. In this case, \texttt{a} can serve as an identifier, and is
provided by the function argument.

@@

Using only \texttt{hoverable}, we are restricted to one element per signal. By
contrast, \texttt{hoverables} permits multiple elements on a single signal. The
hover information of an element can be added to an existing signal, and can even
be added dynamically, that is, when the element is a signal. As the value of a
signal of elements changes, we attach the hover information to the each new
element without having to create a new output signal. We do this by partially
applying \texttt{pool.hoverable} to \texttt{id} purely, and then lifting it on
to the argument.
